Supplementary Informations to Ion pairing controls rheological properties of ``crocodile-line'' polyelectrolyte hydrogels

### 2016-02-01 PALSE/ion_pairing_SI.tex
frequency sweep figure

>>>>

\begin{figure}
\includegraphics{frequency.pdf}
\caption{Storage modulus $G^\prime$ (filled symbols) and loss modulus $G^{\prime\prime}$ (open symbols) measured through oscillatory shear experiments plotted against the frequency $f$ for (a) \ce{PPyr+Cl-} (\textcolor{lightgray}{$\bullet$}), \ce{PPyr+Br-} (\textcolor{gray}{$\blacksquare$}) and \ce{PPyr+I-} ($\blacktriangle$), (b) \ce{PIm+I-} ($\blacktriangledown$) and \ce{PPyr+I-} ($\blacktriangle$) and (c) \ce{PIm+Br-} (\textcolor{gray}{$\blacklozenge$}) and \ce{PPyr+Br-} (\textcolor{gray}{$\blacksquare$}). The fixed strain amplitude is frequency $\gamma=0.1\%$. All samples are at 8\%wt }
\label{fig:frequency}
\end{figure}
